---
title: "Interaktiv sjekk av fil"
author: "Vegard"
date: "2022-09-29"
output: html_document
---

Last updated: 09.12.2022

- This document contain useful functions for exploration of data files
- Alternative to open the file in Excel
- This document should only be used interactively when needed, not saved as report.
- Code chunks may contain several alternative functions. 
    - Run individual functions by placing cursor within function and press Ctrl + Enter . 

Run this to load functions: 

```{r, include=FALSE, message=FALSE}
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
```


# Load data

* Load data file into environment
* For KUBE files in DATERT or NESSTAR-folders, the ReadFile function may be used. 
* For other files (.csv or .rds), use the other functions

```{r}
# KUBE files in DATERT or NESSTAR-folders
data <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH", # KH or NH
                  folder = "2023") # "DATERT" or 4-digit year if file in NESSTAR-folder

# Other CSV files
data <- fread("F:/Forskningsprosjekter/PDB 2455 - Helseprofiler og til_/PRODUKSJON/ORGDATA/SSB/ENEFHIB/ORG/2023/ENEFHIB.csv")

# .Rda-files

data <- readRDS("F:/Forskningsprosjekter/PDB 2455 - Helseprofiler og til_/PRODUKSJON/PRODUKTER/MELLOMPROD/R/STABLAORG/DATERT/TRANGBODDHET_2022-11-07-18-38.rds")


```

# Show full data

* Scrollable table

```{r include = F, eval = F}
data 

# To show in separate (larger) window 
View(data)
```

# Boxplot checks, useful functions

## Show time series

### One strata

- For boxplot checks
- The new data file must be loaded (see methods above)
- Plots the time series for one specific strata
- Specify all dimensions so only one level is selected
    - If NULL, the total group will be selected by default if the dimension exists
    for non-standard dimensions. A message will indicate which group was selected
    .
```{r message=FALSE, warning=FALSE}
ShowTS(data = data, # Name of data object
       maltall = "MEIS", # Value to plot on y-axis
       geo = 0, # NUMERIC: e.g. 0
       alder = "75_120", # INTERVAL: XX_YY, e.g. "0_120"
       kjonn = 2, # NUMERIC: 0, 1, or 2
       utdann = NULL, # NUMERIC
       innvkat = NULL, # NUMERIC
       landbak = NULL, # NUMERIC
       extradim = "KODEGRUPPE", # e.g. "KODEGRUPPE"
       extraval = "Pas_med_hjerteinfarkt", # e.g. "Dod_med_hjerteinfarkt"
       tab = T) # Prints table, change to FALSE if you only want the plot
```

### Multiple strata

- Useful if you want to see the time series for several or all age groups, all genders, all diagnoses etc for one strata. 
- When providing a list of GEO-codes, this can be a shortcut to check all outlier GEO-codes in one strata

```{r message=FALSE, warning=FALSE}
# Create multiple plots
# On first row, enter a dimension to plot one time series for each level, or a list of levels you want to plot for one dimension (e.g. list of GEO). 
# On the corresponding row, input is replaced with ".x", to make one plot per element of the input list. 

# ".x" should be typed without quotes

walk(c(30101, 30102, 30102), # Select dimension or enter list of valid values here as `walk(DIMNAME)' or 'walk(c(a, b, c)' 
    ~ShowTS(data = data, 
            maltall = "MEIS", 
            geo = .x, # Insert .x to refer to the list added above 
            alder = "0_74", 
            kjonn = 1, 
            utdann = NULL, 
            innvkat = NULL, 
            landbak = NULL, 
            extradim = "KODEGRUPPE", # If the selected dimension is the extradimension, extraval must be ".x"
            extraval = "Tot_hjerneslag", # If the list is several diagnoses, ".x" also goes here.
            tab = FALSE)) # Change to TRUE if you also want to see the data
```

# Bydelsplott

## Show bydelsdata

- Prints a table with one row per value column per bydel, one column per year
- For existing dimensions where level is not specified, all levels are included in the table and can be filtered interactively in the output table
    - The more filters you specify, the quicker the function will run
    

```{r fig.height = 10}
ShowBydel(data = data, 
          maltall = c("SPVFLAGG", "MEIS", "TELLER"), # List of value columns to include, e.g. c("SPVFLAGG", "TELLER", "NEVNER"). If NULL, a default selection is shown.
          kommune = NULL, 
          alder = NULL, 
          kjonn = NULL, 
          utdann = NULL,
          innvkat = NULL,
          landbak = NULL,
          extradim = NULL,
          extraval = NULL)
```

# Check if two objects are identical

* Check if two objects (e.g. data files) are identical
* Insert name of the objects to be compared
* Returns TRUE or FALSE

```{r}
identical(object1, object2)
```





