---
title: "Kvalitetskontroll del 1: manuell"
author: ""
date: "`r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
```

```{r echo = F}
## Load data
dfnew <- ReadFile(file = "HKR_2022-09-27-16-27", # Matching, if >1 file found in folder, specify file name further
                  bank = "KH", # KH or NH
                  folder = "DATERT") # "DATERT" or 4-digit year if file in NESSTAR-folder

dfold <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  bank = "KH",# KH or NH
                  folder = 2022) # DATERT" or 4-digit year if file in NESSTAR-folder
```
```{r include=FALSE}
####
# To get a list of variable names in KUBE, run the following code
names(dfnew)
###

# Standard dimensions, entered as c("dim1", "dim2", etc).
STANDARDdims <- c("GEO", "AAR", "KJONN", "ALDER") 

# Extra dimensions, entered as c("dim1", "dim2", etc).
# If no additional dimensions are present/wanted, this should be "EXTRAdims <- NULL"
EXTRAdims <- c("KODEGRUPPE") 

# Value column for censoring (PRIKKING), and the limit 
PRIKKval <- "sumTELLER"
PRIKKlimit <- 12

# For comparison between BYDEL, FYLKE, and LAND, specify which variable to sum
COMPAREval <- "sumTELLER" 

# For grouping output, entered as c("dim1", "dim2", etc).
# Applies to comparisons of censored observations, and between GEOlevels
# If you only want total numbers, this should be "GROUPdims <- NULL"
GROUPdims <- c("KODEGRUPPE", "AAR") 
```

# 1. Compare dimensions

Outputs for the following dimensions: `r print_dim(c(STANDARDdims, EXTRAdims))`
- Number of levels
- New levels (not found in old KUBE)
- Expired levels (not found in new KUBE)

```{r}
CompareDims()
```

# 2. Compare number of PRIKK

- Summarises number of censored rows (SPVFLAGG = 0,1,2,3) in the new and old KUBE, grouped by: `r print_dim(GROUPdims)`
-   **Absolute** (new - old KUBE) and **relative** (new/old cube) difference is calculated and provided per group.
- **NB:** Compares the new and old KUBE directly, including all new or expired levels (e.g. new year, new age groups, etc, are included in the comparison).

```{r}
ComparePrikk()
```

# 3. Are all values below the limit censored?

-   Checks whether all values of `r PRIKKval` <= `r PRIKKlimit`
-   If everything is ok, the function returns a confirmation.
-   If some values at or below PRIKKlimit is present, the corresponding rows are printed for inspection.

```{r}
CheckPrikk()
```

# 4. Does FYLKE sum to LAND?

-   Summarise the column **`r COMPAREval`** for LAND and FYLKE, grouped by: `r print_dim(GROUPdims)`
-   HELSEREGION is excluded from the comparison
-   Calculate the absolute (LAND - FYLKE) and relative (LAND/FYLKE) difference
-   Orders the input according to the relative difference.

```{r}
CompareLandFylke()
```

# 5. Does BYDEL sum to KOMMUNE?

-   Summarise the column **`r COMPAREval`** for KOMMUNE and BYDEL, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.

```{r}
CompareBydelKommune() 
```

# 6. Oslo KOMMUNE = Oslo FYLKE?

-   Summarise the column **`r COMPAREval`** for Oslo kommune and Oslo fylke, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.

```{r}
CompareOslo()
```
