---
title: "Kvalitetskontroll del 2: compare"
author: ""
date: "`r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
<style type="text/css">
.main-container {
  max-width: 80% !important;
  margin: auto;
}
</style>

Version: 1.3.1 (08.05.2023). 

For more info about the quality control, see [here](https://helseprofil.github.io/manual/faq-khvalitetskontroll.html)!

```{r include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/load_packages_functions.R")
```

# INPUT

```{r loadfiles}
# Loads both new file (dfnew), and old file (dfold) for comparison. 
# dfnew and dfold must be provided as full kubename_datotag
# foldernew and folderold must be QC, DATERT or 4-digits
# By default, the following column names are automatically renamed: "antall", "Crude", "Adjusted", "sumteller", "sumnevner", "smr", "FLx", "utdanningsnivå" (only for R version < 4.2)

ReadFiles(dfnew = "FILENAME", # FILENAME with full date tag e.g. KUBENAVN_YYYY-MM-DD-hh-dd
          foldernew = "QC", # QC, DATERT, 4-digit referring to NESSTAR-folder, or foldername (e.g. "KH2024NESSTAR_pre2024_omkod2024GEO")
          modusnew = "KH", # KH or NH
          dfold = "FILENAME", # NULL, or FILENAME with full date tag e.g. KUBENAVN_YYYY-MM-DD-hh-dd
          folderold = "2023", # NULL, or QC, DATERT, 4-digit referring to NESSTAR-folder, or foldername (e.g. "KH2024NESSTAR_pre2024_omkod2024GEO")
          modusold = "KH") # NULL, or KH or NH
```

```{r colnamechange}
# OPTIONAL, MANUAL RENAMING OF COLUMN NAMES
# If dfnew or dfold still contains unwanted column names, which can be checked by names(dfnew) or names(dfold), this can be manually changed by editing `old` and `new` arguments in the the code below:

# NB: Norwegian characters in file name may fail if you use R version 4.2+. In that case, use column position (numeric) to indicate old name (e.g. 1 = first column, be careful to select the correct column!).
# NB2: the function matches the old and new list by position, so old name #1 is replaced with new name #1 etc. 

# New file
RenameColumns(dfnew, 
              old = NULL, # NULL, "old name" OR c("old name 1", "old name 2", etc), OR column position (numeric)
              new = NULL) # NULL, "new name" OR c("new name 1", "new name 2", etc)

# Old file
# Code is skipped if dfold does not exist, no need to comment/uncomment. 
if(exists("dfold")){
RenameColumns(dfold, 
              old = NULL, # NULL, "old name" OR c("old name 1", "old name 2", etc), OR column position (numeric)
              new = NULL) # NULL, "new name" OR c("new name 1", "new name 2", etc) 
}
```

```{r}
# UPDATE 18.01.2022: "<-" is replaced with "<<-" to make sure these settings are applied when saving the report. 

# To save files and report in correct folder
PROFILEYEAR <<- 2024

# To save .csv-files of the flagged KUBEs, and/or the combined compareKUBE, use this option
# Available options: "dfnew_flag", "dfold_flag", and "compareKUBE"
# For no dumps, replace with "DUMPS <<- NULL"
DUMPS <<- c("dfnew_flag", "dfold_flag", "compareKUBE")
```

# Data formatting

- Create flagged versions of new and old KUBE, according to strata defined by all dimension columns
    - Flags all **new** rows in the new KUBE (strata not present in old KUBE)
    - Flags all **expired** rows in the old KUBE (strata not present in the new KUBE)
- Create combined data for comparisons, merged on the common dimensions in new and old KUBE
    - Removes any new or expired row
    - All value columns get the suffix "_new" or "_old"

```{r}
# No arguments needed, everything is defined in INPUT
# If file name is too long, or file name for other reasons should not be the default, there are three name arguments that can be used:
# dfnew_flag_name
# dfold_flag_name
# compareKUBE_name
# Example: FormatData(dfnew_flag_name = "mynewkubename", compareKUBE_name = "mycomparekube")
# By default, outliers (and previous outlier) are flagged. If GEO is different between files, this throws an error. If so, use the argument outlier = FALSE to turn of outlier detection.
FormatData()
```

# Compare

## Summary table

- In the compareKUBE, calculate per value column per geographical level:
    - N identical: How many rows are identical (same value or both censored)
    - N new prikk: How many rows are censored in the new file, but not in the old
    - N exp prikk: How many rows were censored in the old file, but no longer in the new
    - N different: How many rows are different (with both new and old value present)
- For different columns (not total data set), calculate
    - Absolute difference: Mean, minumum, and maximum (new - old)
    - Relative difference: Mean, minimum, and maximum ratio (new / old) 
    
```{r}
CompareDiffRows()
```

## Time trends in diffs
```{r fig.width=11}
PlotTimeDiff()
```


```{r eval = F}
# Save report (instead of using the knit button)
# Run code to save HTML-report to F:/...PRODUKSJON/VALIDERING/NESSTAR_KUBER/9999(profile year)/KVALITETSKONTROLL/KUBENAVN/
# Make sure PROFILEYEAR is correctly defined in INPUT section
# If the file name becomes too long, you can set shortname = TRUE, and only the datetag will be used as file name, e.g. XXXX-XX-XX-XX-XX_Kvalitetskontroll_del1.html. 
# If savename = NULL, file name will default to the full cube name (incl date tag). You can also manually select the name of the output file. 

# NB: 
# You must load data files before saving the report
# You must ALSO save the document (Ctrl + S) before saving the report using this function!

SaveReport(profileyear = PROFILEYEAR,
           inputfile = "Kvalitetskontroll_del2.Rmd",
           shortname = FALSE,
           savename = NULL)
```
