---
title: "Kvalitetskontroll del 2: compare"
author: ""
date: "`r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
<style type="text/css">
.main-container {
  max-width: 80% !important;
  margin: auto;
}
</style>
Version: 1.2.1 (18.01.2022). 

For more info about the quality control, see [here](https://github.com/helseprofil/KHvalitetskontroll)!

```{r include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
```

# INPUT

*New file:* 
```{r echo = F}
## Load new data file
dfnew <- ReadFile(file = "FILENAME", # Matching, if >1 file found in folder, specify file name further. Example: "KUHR_2022-11-23-15-11"
                  modus = "KH", # KH or NH
                  folder = "DATERT") # "DATERT" or 4-digit year if file in NESSTAR-folder

####
# To get a list of variable names in the new KUBE, uncomment and run the following code: 
# names(dfnew)
###

# To chance column names, uncomment and edit the following:
# setnames(dfnew, old = "OLD NAME", new = "NEW NAME", skip_absent = TRUE)

# Default list is set for column names which often needs to be changed.
# NB: Norwegian characters in file name may fail if you use R version 4.2. In that case, use column position to indicate old name.
setnames(dfnew, 
         old = c("antall", "crude", "Adjusted", "sumteller", "sumnevner", "smr", "FLx", "utdanningsnivå"),
         new = c("TELLER", "RATE", "MEIS", "sumTELLER", "sumNEVNER", "SMR", "MEIS", "UTDANN"),
         skip_absent = TRUE)
```

*Old file for comparison:*
```{r}
# Load old data file
dfold <- ReadFile(file = "FILENAME", # Matching, if >1 file found in folder, specify file name further. Example: "KUHR_2022-11-23-15-11"
                  modus = "KH",# KH or NH
                  folder = "2022") # DATERT" or 4-digit year if file in NESSTAR-folder

####
# To get a list of variable names in the old KUBE, uncomment and run the following code: 
# names(dfold)
###

# To chance column names, uncomment and edit the following:
# setnames(dfold, old = "OLD NAME", new = "NEW NAME", skip_absent = TRUE)

# Default list is set for column names which often needs to be changed.
# NB: Norwegian characters in file name may fail if you use R version 4.2. In that case, use column position to indicate old name.
setnames(dfold, 
         old = c("antall", "crude", "Adjusted", "sumteller", "sumnevner", "smr", "FLx", "utdanningsnivå"),
         new = c("TELLER", "RATE", "MEIS", "sumTELLER", "sumNEVNER", "SMR", "MEIS", "UTDANN"),
         skip_absent = TRUE) 
```

```{r}
# UPDATE 18.01.2022: "<-" is replaced with "<<-" to make sure these settings are applied when saving the report. 

# To save files and report in correct folder
PROFILEYEAR <<- 2023

# To save .csv-files of the flagged KUBEs, and/or the combined compareKUBE, use this option
# Available options: "dfnew_flag", "dfold_flag", and "compareKUBE"
# For no dumps, replace with "DUMPS <<- NULL"
DUMPS <<- c("dfnew_flag", "dfold_flag", "compareKUBE")
```

# Data formatting

- Create flagged versions of new and old KUBE, according to strata defined by all dimension columns
    - Flags all **new** rows in the new KUBE (strata not present in old KUBE)
    - Flags all **expired** rows in the old KUBE (strata not present in the new KUBE)
- Create combined data for comparisons, merged on the common dimensions in new and old KUBE
    - Removes any new or expired row
    - All value columns get the suffix "_new" or "_old"

```{r}
# No arguments needed, everything is defined in INPUT
# If file name is too long, or file name for other reasons should not be the default, the three _name-arguments can be specified. 
# Example: dfnew_flag_name = "your preferred filename"
FormatData(dfnew_flag_name = NULL,
           dfold_flag_name = NULL,
           compareKUBE_name = NULL)
```

# Compare

## Summary table

- In the compareKUBE, calculate per value column per geographical level:
    - N identical: How many rows are identical (same value or both censored)
    - N new prikk: How many rows are censored in the new file, but not in the old
    - N exp prikk: How many rows were censored in the old file, but no longer in the new
    - N different: How many rows are different (with both new and old value present)
- For different columns (not total data set), calculate
    - Absolute difference: Mean, minumum, and maximum (new - old)
    - Relative difference: Mean, minimum, and maximum ratio (new / old) 
    
```{r}
CompareDiffRows(data = compareKUBE)
```

## Time trends in diffs
```{r fig.width=11}
PlotTimeDiff(data = compareKUBE)
```


```{r eval = F}
# Save report (instead of using the knit button)
# Run code to save HTML-report to F:/...PRODUKSJON/VALIDERING/NESSTAR_KUBER/9999(profile year)/KVALITETSKONTROLL/KUBENAVN/
# Profile year is defined in input
# If savename = NULL, file name will default to the full cube name (incl date tag)

# NB: You must load the data files AND save the source file (Ctrl + S) before creating the HTML report using this function!

SaveReport(profileyear = PROFILEYEAR,
           inputfile = "Kvalitetskontroll_del2.Rmd",
           savename = NULL)
```
