---
title: "Kvalitetskontroll del 2: compare"
author: ""
date: "`r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
Version: 1.0 (15.12.2022). 

For more info about the quality control, see [here](https://github.com/helseprofil/KHvalitetskontroll)!

```{r include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
```

# INPUT

*New file:* 
```{r echo = F}
## Load new data file
dfnew <- ReadFile(file = "KUHR_2022-11-23-15", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH", # KH or NH
                  folder = "DATERT") # "DATERT" or 4-digit year if file in NESSTAR-folder

####
# To get a list of variable names in the new KUBE, uncomment and run the following code: 
# names(dfnew)
###
```

*Old file for comparison:*
```{r}
# Load old data file
dfold <- ReadFile(file = "KUHR", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH",# KH or NH
                  folder = "2022") # DATERT" or 4-digit year if file in NESSTAR-folder

####
# To get a list of variable names in the old KUBE, uncomment and run the following code: 
# names(dfold)
###
```

```{r}
# To save files and report in correct folder
PROFILEYEAR <- 2023
####

# To save .csv-files of the flagged KUBEs, and/or the combined compareKUBE, use this option
# Available options: "dfnew_flag", "dfold_flag", and "compareKUBE"
# For no dumps, replace with "DUMPS <- NULL"
DUMPS <- NULL #c("dfnew_flag", "compareKUBE", "dfold_flag")
```

# Data formatting

- Create flagged versions of new and old KUBE, according to strata defined by all dimension columns
    - Flags all **new** rows in the new KUBE (strata not present in old KUBE)
    - Flags all **expired** rows in the old KUBE (strata not present in the new KUBE)
- Create combined data for comparisons, merged on the common dimensions in new and old KUBE
    - Removes any new or expired row
    - All value columns get the suffix "_new" or "_old"

```{r}
# No arguments needed, everything is defined in INPUT
FormatData()
```

# Compare

## Summary table

- In the compareKUBE, calculate per value column per geographical level:
    - N identical: How many rows are identical (same value or both censored)
    - N new prikk: How many rows are censored in the new file, but not in the old
    - N exp prikk: How many rows were censored in the old file, but no longer in the new
    - N different: How many rows are different (with both new and old value present)
- For different columns (not total data set), calculate
    - Absolute difference: Mean, minumum, and maximum (new - old)
    - Relative difference: Mean, minimum, and maximum ratio (new / old) 
    
```{r}
CompareDiffRows(data = compareKUBE)
```

## Time trends in diffs
```{r fig.width=10}
PlotTimeDiff(data = compareKUBE)
```


```{r eval = F}
# Save report (instead of using the knit button)
# Run code to save HTML-report to F:/...PRODUKSJON/VALIDERING/NESSTAR_KUBER/9999(profile year)/KVALITETSKONTROLL/KUBENAVN/
# Profile year is defined in input
# If savename = NULL, file name will default to the full cube name (incl date tag)

# NB: You must save the source file (Ctrl + S) before saving the report using this function!

SaveReport(profileyear = PROFILEYEAR,
           inputfile = "Kvalitetskontroll_del2.Rmd",
           savename = NULL)
```
