---
title: "Kvalitetskontroll del 1: manuell"
author: ""
date: "Report generated: `r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
Version: 1.3 (07.11.2022). 

For more info about the quality control, see [here](https://github.com/helseprofil/KHvalitetskontroll)!
```{r setup, include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
```

# INPUT

**Data files loaded: **
```{r echo = F}
## Load data
dfnew <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH", # KH or NH
                  folder = 2023) # "DATERT" or 4-digit year if file in NESSTAR-folder

dfold <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH",# KH or NH
                  folder = 2022) # DATERT" or 4-digit year if file in NESSTAR-folder
```
**Input parameters: **
```{r include=FALSE}
####
# To get a list of variable names in the new and old KUBE, run the following code
names(dfnew)
names(dfold)
###

# To save files and report in correct folder
PRODUCTIONYEAR <- 2023

# Standard dimensions, entered as c("dim1", "dim2", etc).
STANDARDdims <- c("GEO", "AAR", "KJONN", "UTDANN", "INNVKAT") 

# Extra dimensions, entered as c("dim1", "dim2", etc).
# If no additional dimensions are present/wanted, this should be "EXTRAdims <- NULL"
EXTRAdims <- "KODEGRUPPE"

# Value column for censoring (PRIKKING), and the limit to check against
# If no limit is set, the value of these can be NA (missing): "PRIKKval = NA", "PRIKKlimit = NA"
PRIKKval <- "sumTELLER"
PRIKKlimit <- 12

# For comparison between BYDEL, FYLKE, and LAND, specify which variable to sum
COMPAREval <- "sumTELLER" 

# For grouping output, entered as c("dim1", "dim2", etc).
# Applies to comparisons of censored observations, and between GEOlevels
# If you only want total numbers, this should be "GROUPdims <- NULL"
GROUPdims <- c("KODEGRUPPE", "AAR", "ALDER") 

# Time series plots
# Generates one plot per PLOTDIMS, and each plot contains a panel per PLOTTVALS
# Currently accepts the following dimensions: "KJONN", "UTDANN", "INNVKAT", "LANDBAK", and all "EXTRAdims"
# Totals are kept for dimensions other than the one being plotted. For extra dimensions, plotvals are added (TELLER/sumTELLER) or averaged (not TELLER/sumTELLER)
PLOTDIMS <- c("KJONN", "KODEGRUPPE")
PLOTVALS <- c("sumTELLER", "sumNEVNER")
```

```{r}
# To print input, do not change:
cat("Standard dimensions: ", print_dim(STANDARDdims), 
    "\nExtra dimensions: ", print_dim(EXTRAdims),
    "\nValue to check for prikking: ", print_dim(PRIKKval),
    "\nLimit for prikking: ", PRIKKlimit,
    "\nValue to compare between geolevels: ", print_dim(COMPAREval), 
    "\nDimensions to group output by: ", print_dim(GROUPdims))
```

# 1. Compare columns

- Check whether there are any new columns (not present in the old kube)
- Check if there are any expired columns (not present in the new kube)

```{r}
CompareCols()
```

# 2. Compare dimensions

Outputs for the following dimensions: `r print_dim(c(STANDARDdims, EXTRAdims))`

- Number of levels
- New levels (not found in old KUBE)
- Expired levels (not found in new KUBE)

```{r}
# If any dimensions are identified as new or expired columns (i.e. not present in both files), they will not be evaluated

CompareDims()
```

# 3. Compare number of consored observations

- Summarises number of censored rows (SPVFLAGG = 0,1,2,3) in the new and old KUBE, grouped by: `r print_dim(EXTRAdims)`
-   **Absolute** (new - old KUBE) and **relative** (new/old cube) difference is calculated and provided per group.
- **NB:** Compares the new and old KUBE directly, including all new or expired levels (e.g. new year, new age groups, new geolevels, etc, are included in the comparison).
-   Use search bar to filter out rows of interest (e.g only show SPVFLAGG=3)

```{r}
# Default is to stratify the output by EXTRAdims (input)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: ComparePrikk(groupdim = c("AAR", "ALDER", "etc"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  

ComparePrikk(groupdim = EXTRAdims)
```

# 4. Are all values below the limit censored?

-   Checks whether all values of `r PRIKKval` <= `r PRIKKlimit`
-   If everything is ok, the function returns a confirmation.
-   If some values at or below PRIKKlimit is present, the corresponding rows are printed for inspection.

```{r}
CheckPrikk()
```

# 5. Does FYLKE sum to LAND?

-   Summarise the column **`r COMPAREval`** for LAND and FYLKE, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (LAND - FYLKE) and relative (LAND/FYLKE) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest (e.g. only show specific year)

```{r}
# Default is to stratify the output by GROUPdims (input)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: ComparePrikk(groupdim = c("AAR", "ALDER", "etc"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  

CompareLandFylke(groupdim = GROUPdims)
```

# 6. Does BYDEL sum to KOMMUNE?

-   Summarise the column **`r COMPAREval`** for KOMMUNE and BYDEL, grouped by: `r print_dim(GROUPdims)`
-   Calculated for Oslo, Bergen, Trondheim, and Stavanger.
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest (e.g. only show Oslo or specific year)

```{r}
# Default is to stratify the output by GROUPdims (input)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: ComparePrikk(groupdim = c("AAR", "ALDER", "etc"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  

CompareBydelKommune(groupdim = GROUPdims)
```

# 7. Oslo KOMMUNE = Oslo FYLKE?

-   Summarise the column **`r COMPAREval`** for Oslo kommune and Oslo fylke, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest (e.g. only show specific year)

```{r}
# Default is to stratify the output by GROUPdims (input)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: ComparePrikk(groupdim = c("AAR", "ALDER", "etc"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  

CompareOslo(groupdim = GROUPdims)
```

# 8. Country level time-series plots
```{r fig.height=8}
PlotTimeseries()
```


```{r eval = F}
# Save report (instead of using the knit button)
# Run code to save HTML-report to F:/...PRODUKSJON/VALIDERING/NESSTAR_KUBER/9999(production year)/KVALITETSKONTROLL/KUBENAVN/
# Make sure productionyear is correctly defined in INPUT section
# If savename = NULL, file name will default to the full cube name (incl date tag)

# NB: 
# You must run the INPUT section before saving the report, to generate all the objects
# You must ALSO save the document (Ctrl + S) before saving the report using this function!

SaveReport(productionyear = PRODUCTIONYEAR, 
           inputfile = "Kvalitetskontroll_del1.Rmd",
           savename = "TEST0711_2")
```

