---
title: "Kvalitetskontroll"
author: ""
date: "`r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
```

```{r echo = F}
## Load data
dfnew <- ReadFile(file = "HKR_2022-09-27-16-27", # Matching, if >1 file found in folder, specify file name further
                  bank = "KH", # KH or NH
                  folder = "DATERT") # "DATERT" or 4-digit year if file in NESSTAR-folder

dfold <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  bank = "KH",# KH or NH
                  folder = 2022) # DATERT" or 4-digit year if file in NESSTAR-folder
```


```{r include=FALSE}
####
# To get a list of variable names in KUBE, run the following
names(dfnew)
###

STANDARDdims <- c("GEO", "AAR", "KJONN", "ALDER")
EXTRAdims <- c("KODEGRUPPE") # If no additional dimensions ar present, this should be "EXTRAdims <- NULL"

PRIKKval <- "sumTELLER"
PRIKKlimit <- 12

COMPAREval <- "sumTELLER"
GROUPdims <- c("KODEGRUPPE", "AAR") # If you only want total numbers, this should be "GROUPdims <- NULL"
```


# 1. Compare dimensions

-   The function compares the levels within dimensions defined under INPUT as `STANDARDdims`and `EXTRAdims`.

[**Output:**]{.underline}

-   Number of levels in each dimension (new KUBE)
-   New levels, which did not exist in previous KUBE
-   Expired levels, which existed in previous KUBE, but not in the new KUBE. **NB: Should these be present?**

```{r}
CompareDims()
```

# 2. Compare number of PRIKK

-   Calculates the amount of cencored observations in new and old KUBE, grouped by type of SPVFLAGG and the `GROUPdims` as defined in `Input`. If `GROUPdims <- NULL`, output is only grouped by type of SPVFLAGG.
-   Absolute (new - old KUBE) and relative (new/old cube) difference is calculated and given per group.

```{r}
ComparePrikk()
```

# 3. Are all values below the limit censored?

-   Checks whether all values of `PRIKKval` \<= `PRIKKlimit`, as defined in `Input`
-   If everything is ok, the function returns a confirmation.
-   If some values at or below PRIKKlimit is present, the corresponding rows are printed for inspection.

```{r}
CheckPrikk()
```

# 4. Does FYLKE sum to LAND?

-   Summarise the column **`r COMPAREval`** for LAND and FYLKE, grouped by: **`r str_c(GROUPdims, collapse = ", ")`**
-   HELSEREGION is excluded from the comparison
-   Calculate the absolute (LAND - FYLKE) and relative (LAND/FYLKE) difference
-   Orders the input according to the relative difference.

```{r}
CompareLandFylke()
```

# 5. Does BYDEL sum to KOMMUNE?

-   Summarise the column **`r COMPAREval`** for KOMMUNE and BYDEL, grouped by: **`r str_c(GROUPdims, collapse = ", ")`**
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.

```{r}
CompareBydelKommune() 
```

# 6. Oslo KOMMUNE = Oslo FYLKE?

-   Summarise the column **`r COMPAREval`** for Oslo kommune and Oslo fylke, grouped by: **`r str_c(GROUPdims, collapse = ", ")`**
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.

```{r}
CompareOslo()
```
