---
title: "Kvalitetskontroll del 1: manuell"
author: ""
date: "Report generated: `r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
<style type="text/css">
.main-container {
  max-width: 80% !important;
  margin: auto;
}
</style>

Version: 1.9.5 (09.11.2023). 

For more info about the quality control, see [here](https://helseprofil.github.io/manual/faq-khvalitetskontroll.html)!
```{r init, include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
# Only run if functions are not already loaded. 
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/load_packages_functions.R")
```

# COMMENTS

- 
- 
-

# INPUT

**Data files loaded**
```{r loadfiles}
# Loads both new file (dfnew), and old file (dfold) for comparison. 
# dfnew and dfold must be provided as full kubename_datotag
# foldernew and folderold must be QC, DATERT or 4-digits
# By default, the following column names are automatically renamed: "antall", "NULL, Crude", "Adjusted", "sumteller", "sumnevner", "smr", "FLx", "utdanningsnivå" (only for R version < 4)

ReadFiles(dfnew = "FILENAME", # FILENAME with full date tag e.g. KUBENAVN_YYYY-MM-DD-hh-dd
          foldernew = "QC", # QC, DATERT, 4-digit referring to NESSTAR-folder, or foldername (e.g. "KH2024NESSTAR_pre2024_omkod2024GEO")
          modusnew = "KH", # KH or NH
          dfold = "FILENAME", # NULL, or FILENAME with full date tag e.g. KUBENAVN_YYYY-MM-DD-hh-dd
          folderold = "2023", # NULL, or QC, DATERT, 4-digit referring to NESSTAR-folder, or foldername (e.g. "KH2024NESSTAR_pre2024_omkod2024GEO")
          modusold = "KH", # NULL, or KH or NH
          recodeold = FALSE, # Should GEO-codes in old files be recoded to comply with current GEO?
          recodenew = FALSE) # Should GEO-codes in new files be recoded to comply with current GEO?
```

```{r colnamechange, echo = F}
# OPTIONAL, MANUAL RENAMING OF COLUMN NAMES
# If dfnew or dfold still contains unwanted column names, which can be checked by names(dfnew) or names(dfold), this can be manually changed by editing `old` and `new` arguments in the the code below:

# NB: Norwegian characters in file name may fail if you use R version 4.2+. In that case, use column position (numeric) to indicate old name (e.g. 1 = first column, be careful to select the correct column!).
# NB2: the function matches the old and new list by position, so old name #1 is replaced with new name #1 etc. 

# New file
RenameColumns(dfnew, 
              old = NULL, # NULL, "old name" OR c("old name 1", "old name 2", etc), OR column position (numeric)
              new = NULL) # NULL, "new name" OR c("new name 1", "new name 2", etc)

# Old file
# Code is skipped if dfold does not exist, no need to comment/uncomment. 
if(exists("dfold")){
RenameColumns(dfold, 
              old = NULL, # NULL, "old name" OR c("old name 1", "old name 2", etc), OR column position (numeric)
              new = NULL) # NULL, "new name" OR c("new name 1", "new name 2", etc) 
}
```

**Input parameters: **
```{r input, echo = T}
# To save files and report in correct folder
PROFILEYEAR <<- 2024

# Value column for censoring (PRIKKING), and the limit to check against
# If no limit is set, the value of these can be NA (missing): "PRIKKval <<- NA", "PRIKKlimit <<- NA"
PRIKKval <<- "sumTELLER"
PRIKKlimit <<- 12

# For grouping output, entered as c("dim1", "dim2", etc).
# Applies to comparisons of censored observations (2B), and between GEOlevels (3A-D)
# If you only want total numbers, this should be "GROUPdims <<- NULL"
# Can also be edited directly in the code chunks if you want different grouping
GROUPdims <<- c("AAR") 

# If you don't want to compare across GEOlevels (Fylke vs Land etc), set this option to FALSE. 
CompareGEO <<- TRUE
```

# 1. Compare columns and dimensions

## 1A. Compare columns
- Check whether there are any new columns (not present in the old kube)
- Check if there are any expired columns (not present in the new kube)
- Check if new kube have uncensored sumTELLER, sumNEVNER, and RATE.n
- If only one file, list column names.

```{r comparecols}
CompareCols()
```

## 1B. Compare dimensions

- Number of levels per dimension
- New levels (not found in old KUBE)
- Expired levels (not found in new KUBE)
- If only one file, only number of levels per dimension.

```{r comparedims}
CompareDims()
```

# 2. Check censoring

## 2A. Are all values below the limit censored?

-   Checks whether all values of `r PRIKKval` <= `r PRIKKlimit`
-   If everything is ok, the function returns a confirmation.
-   If some values at or below PRIKKlimit is present, the corresponding rows are printed for inspection in a separate window.

```{r checkprikk}
CheckPrikk()
```

## 2B. Compare number of censored observations

- Summarises number of rows that are uncensored (SPVFLAGG = 0) and censored (SPVFLAGG = 1, 2, or 3) in the new and old KUBE
-   **Absolute** (new - old KUBE) and **relative** (new/old cube) difference is calculated and provided per group.
- If only one file, results for this file shown

```{r compareprikk}
# For groupdims, only levels included in dfnew is shown

# Tips: for expired levels not included in GROUPdims, it can be useful to remove them before comparison. 
# To remove them from dfold, you can specify the data2-argument like this and filter out expired strata:
# ComparePrikk(data2 = dfold[!GEO %in% 81:84]) - removes helseregion from dfold (includes all GEO not in 81-84)
# ComparePrikk(data2 = dfold[AAR %in% unique(dfnew$AAR)]) - only include AAR which is also present in dfnew
# ComparePrikk(data2 = dfold[SOES == 0]) - only include SOES = 0 
ComparePrikk()
```

## 2C. Check censoring within each time series

- Across all strata, summarizes number and proportion of time series with 0 (complete), 1, 2, ..., max (all cencored), etc censored observations

```{r prikkts}
# Tips: for expired levels, it can be useful to remove them before comparison. 
# To remove them from dfold, you can specify the data2-argument like this and filter out expired strata
# ComparePrikkTS(data2 = dfold[!GEO %in% 81:84]) - removes helseregion from dfold (includes all GEO not in 81-84)
# ComparePrikkTS(data2 = dfold[AAR %in% unique(dfnew$AAR)]) - only include AAR which is also present in dfnew
# ComparePrikkTS(data2 = dfold[SOES == 0]) - only include SOES = 0 
ComparePrikkTS()
```

# 3. Lower sums up to higher geographical level 

## 3A. Does FYLKE sum to LAND?

-   Summarise sumTELLER_uprikk/sumTELLER/TELLER for LAND and FYLKE, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (LAND - FYLKE) and relative (LAND/FYLKE) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest (e.g. only show specific year)

```{r fylkeland}
# Default is to stratify the output by GROUPdims (input)
# Geolevels are compared on sumTELLER_uprikk > sumTELLER > sumTELLER (first which is present)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: CompareFylkeLand(groupdim = c("AAR", "ALDER", "etc"))
# To mimic the boxplot table, use: CompareFylkeLand(groupdim = c(EXTRAdims, "ALDER", "KJONN"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  
CompareFylkeLand(groupdim = GROUPdims)
```

## 3B. Does KOMMUNE sum to FYLKE?

-   Summarise sumTELLER_uprikk/sumTELLER/TELLER for KOMMUNE and FYLKE, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (FYLKE - KOMMUNE) and relative (FYLKE/KOMMUNE) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest 

```{r kommunefylke}
# Default is to stratify the output by GROUPdims (input).
# Geolevels are compared on sumTELLER_uprikk > sumTELLER > sumTELLER (first which is present)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: CompareKommuneFylke(groupdim = c("AAR", "ALDER", "etc"))
# To mimic the boxplot table, use: CompareKommuneFylke(groupdim = c(EXTRAdims, "ALDER", "KJONN"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  
CompareKommuneFylke(groupdim = GROUPdims)
```

## 3C. Oslo KOMMUNE = Oslo FYLKE?

-   Summarise sumTELLER_uprikk/sumTELLER/TELLER for Oslo kommune and Oslo fylke, grouped by: `r print_dim(GROUPdims)`
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest (e.g. only show specific year)

```{r oslo}
# Default is to stratify the output by GROUPdims (input)
# Geolevels are compared on sumTELLER_uprikk > sumTELLER > sumTELLER (first which is present)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: CompareOslo(groupdim = c("AAR", "ALDER", "etc"))
# To mimic the boxplot table, use: CompareOslo(groupdim = c(EXTRAdims, "ALDER", "KJONN"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  

CompareOslo(groupdim = GROUPdims)
```

## 3D. Does BYDEL sum to KOMMUNE?

-   Summarise sumTELLER_uprikk/sumTELLER/TELLER for BYDEL and KOMMUNE, grouped by: `r print_dim(GROUPdims)`
-   Calculated for Oslo, Bergen, Trondheim, and Stavanger.
-   Calculate the absolute (KOMMUNE - BYDEL) and relative (KOMMUNE/BYDEL) difference
-   Orders the input according to the relative difference.
-   Use search bar to filter out rows of interest (e.g. only show Oslo or specific year)

```{r bydelkommune}
# Default is to stratify the output by GROUPdims (input)
# Geolevels are compared on sumTELLER_uprikk > sumTELLER > sumTELLER (first which is present)

# If you want to group output by other columns, you can specify this explicitly in the groupdim-argument
# Example: CompareBydelKommune(groupdim = c("AAR", "ALDER", "etc"))
# To mimic the boxplot table, use: CompareBydelKommune(groupdim = c(EXTRAdims, "ALDER", "KJONN"))

# NB! In the first bullet point above, the grouping variables are also printed to the report. This can also be modified accordingly: `r print_dim(c("AAR", "ALDER", "etc"))`  

CompareBydelKommune(groupdim = GROUPdims)
```

# 4. Proportion of unspecified BYDEL

- Searchable table summarizing the proportion of unspecified bydel
- Uses value columns containing "TELLER" or "NEVNER"
- Only includes years with data on bydel

```{r unknownbydel}
# When maxrows = TRUE, a maximum of 8000 rows is printed. This reduces file size and make the report faster/more responsive. 
# The top X rows (sorted by "UOPPGITT, %") per MALTALL per KOMMUNE is printed (8000 rows total)
# To print all rows, set maxrows = FALSE
UnspecifiedBydel(maxrows = TRUE)
```


# 5. Country level time-series plots

- Plots country-level time-series data to check for misclassification across dimensions
- For each plot, all dimensions other than the one plotted is aggregated (if total is not present). 

```{r ts1}
# This function creates the country level time series plots for all value columns across all dimensions
# The plots are printed in the next code chunk. This is to be able to adjust the figure height according to number of dimensions
# Summary of aggregation going into the plots
# The plots are stored in an object called `TS` which is stored in the environment. To show plots in plotting window (better resizing), just call TS in the console.
PlotTimeseries()
```
```{r ts2, fig.height = .PlotHeight, out.width = "90%", results = 'asis'}
# This prints the time series plots
PrintTimeseries()
```

```{r eval = F}
# Save report (instead of using the knit button)
# Run code to save HTML-report to F:/...PRODUKSJON/VALIDERING/NESSTAR_KUBER/9999(profile year)/KVALITETSKONTROLL/KUBENAVN/
# Make sure PROFILEYEAR is correctly defined in INPUT section
# If the file name becomes too long, you can set shortname = TRUE, and only the datetag will be used as file name, e.g. XXXX-XX-XX-XX-XX_Kvalitetskontroll_del1.html. 
# If savename = NULL, file name will default to the full cube name (incl date tag). You can also manually select the name of the output file. 

# NB: 
# You must load data files before saving the report
# You must ALSO save the document (Ctrl + S) before saving the report using this function!

SaveReport(profileyear = PROFILEYEAR, 
           inputfile = "Kvalitetskontroll_del1.Rmd",
           shortname = FALSE,
           savename = NULL)
```

