---
title: "Kvalitetskontroll del 2: compare"
author: ""
date: "`r Sys.Date()`"
output:
  html_document: 
    df_print: paged
    toc: true
    toc_float: true
---
For more info about the quality control, see [here](https://github.com/helseprofil/KHvalitetskontroll)!

```{r setup, include=FALSE}
# Global settings, do not change
knitr::opts_chunk$set(cache = F, echo = F)
source("https://raw.githubusercontent.com/helseprofil/KHvalitetskontroll/main/R/setup.R")
#source("../R/functions_step2.R")
```

# INPUT

**Data files loaded**
```{r echo = F}
## Load data
dfnew <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH", # KH or NH
                  folder = 2023) # "DATERT" or 4-digit year if file in NESSTAR-folder

dfold <- ReadFile(file = "HKR", # Matching, if >1 file found in folder, specify file name further
                  modus = "KH",# KH or NH
                  folder = 2022) # DATERT" or 4-digit year if file in NESSTAR-folder
```
```{r}
####
# To get a list of variable names in the new and old KUBE, run the following code
names(dfnew)
names(dfold)
###

# Define all dimensions used to identify new or expired rows in the two KUBEs
DIMENSIONS <- c("GEO", "AAR", "KJONN", "ALDER", "KODEGRUPPE")

# Define all value columns to be compared between the two KUBEs
VALUES <- c("TELLER", "RATE", "SMR", "MEIS", "RATE.n", "sumTELLER", "sumNEVNER")

# If you want to save .csv-files of the flagged KUBEs, define 
# Available options: "dfnew_flag", "dfold_flag"
# For no dumps, replace with "DUMPS <- NULL"
DUMPS <- c("dfnew_flag")
DUMPname <- "HKR" # NAME of KUBE, for naming of dumps
```

```{r}
# To print input, do not change:
cat("DIMENSION columns: ", print_dim(DIMENSIONS), 
    "\nVALUE columns: ", print_dim(VALUES))
```
# Data formatting

- Create flagged versions of new and old KUBE, according to strata defined by the following dimensions: `r print_dim(DIMENSIONS)`
    - Flags all **new** rows in the new KUBE (strata not present in old KUBE)
    - Flags all **expired** rows in the old KUBE (strata not present in the new KUBE)
- Create combined data for comparisons, merged on the common dimensions in new and old KUBE
    - Removes any new or expired row
    - All value columns get the suffix "_new" or "_old"

```{r}
FormatData()
```
# Compare value columns

- For value columns, print table showing absolute and relative diff.
- Search along VALUES
- Is it possible to generate headers and code chunk from VALUES? 
    - Or generate table with one pane per value column?
- Output in sortable table, showing absolute and relative difference 




